---
title: "Hunt Strategy"
author: "Brett Stacy"
date: "23 May 2019"
output: pdf_document
---

```{r, echo=F}
library(casal)
```

## BS 23/07/19: Things to look at if I revisit this discrepency stuff:
  * CatchA frequency matches up with scanned frequency for TOP but not TOA. Is this a problem?
  * Does frequency of scanned fish in \@tag_recapture Tags2005_R1_R1 match fishing selectivity? i.e. does tagging
  selectivity match fishing selectivity?
  * Why does ## set CASAL to calculate SSB after 100% F and M
             para$ass$spawning_part_mort <- 0.5
  work for updated TOP parameters but not for other species like TOA or skipjack tuna?
  * Inspect what this is: para$ass$output$`numbers_at[Numbers_at_age_R1]`$proportion_mortality. Does it have to do/match with      para\$ass\$spawning_part_mort <- 0.5?
  * Inspect datass$spawning_use_total_B
  
  
  
  
  
  
  


## List of To-Do's

  * Build model that generates SSB discrepency
    * Remove all estimated parameters from CASAL except B0
    * Set rec_mu == 1e6
    * Lots of tags
    
  * Extract CASAL arrays
    * catch at age
    * catch at length
    * fish scanned / recaptured
    
  * Compare extracted arrays to catch
  
  * Determine where para$sampling$catchage_N and para$sampling$catchlen_N show up in CASAL output.
  
## Script Tracker
TOA_bug_1.R - TOA just as it was from single_region_TOA_baseline.R
TOA_bug_2.R - TOA script after changing YCS in earthfish to allow different prior bound inputs
TOA_bug_3.R - Skipjack Tuna LHPs
TOA_bug_4.R - TOP with updated LHPs
TOA_bug_5.R - same as TOA_bug_2.R except now implementing equilibrium wind-up years before CASAL assessment.



  
  
## Code questions - Brett
Cannot supress YCS estimation through planetfish.
When I change bounds on YCS prior, they are not reflected in output.log. They remain the same as the default. Why?

Cannot supress q estimation through planetfish. Why?

WOW: PERFORMS BETTER WITH FEWER TAGS! I tried with 25,000 tags, 2,500 tags, 10 tags, and 2 tags. As the tag number decreased, the casal performs better at estimating SSB. Noteably, the estimate is still not good enough. This seems very odd. Perhaps the influence of other information is increasingly more influential as tag number decreases. My understanding is, the only other source of information in the survey is catch-at-age data. Could this truely be what is helping the casal model estimate SSB? And why does increasing the tag frequency hurt instead of help?

Run with low tags and low catchA (10 instead of 1000) data collection:
Performs as accurately as above, but not as precise. This must mean the majority of information contributing to the performance of the casal model is a combination of perfect knowledge of LHPs and catch data?

Run with low tags and low catchA but with TOP Growth. 30 iterations.:
PERFOMS REALLY WELL. 

Run with low tags and low catchA but on single_region_TOP.R:
Performs really BAD. Why would it perform well in last run but not this one? The only difference is the LHPs other than growth. I tried turning off estimating selectivity and it is still bad. I need to figure out what is going on with TOA_bug_1.R; how can it perform well when tags and catchA are reduced to unreasonably low levels?
CONCLUSION: The only evidence I can find that potentially explains the difference in performance between the two scripts is this: In the estimation.csl files, the only recaptured fish are caught earler in the sampling for TOA_bug_1 than in TOP_baseline_Minimum_Sampling (only recaptures for latter script were in 2010, the assessment year). Perhaps the earlier recaptures leads to better SSB quantification.
CONCLUSION: After increasing the tag-years and #tags to 20 in TOP_baseline_Minimum_Sampling, the performance was finally good, and the tag-recaptures happened sooner. This could mean that recaptures early-on are very important?
  
  
  
  
  
Change Growth to TOP:
PERFORMS WELL. => perhaps this is because somewhere along the line, the growth parameters are being used to calculate lengths. If this is happening, the fact that L_inf = 1565 is less than the modeled maximum length could produce problems. Mathematically, converting length to age using the von Bertalanffy relationship requires any length input to be less than L_inf. Otherwise, the log of a negative number is attempted. 


Change Growth to TOA S. Mormede 2015:
PERFORMS BAD.
  
  

Why aren't para\$sampling\$catchlen_N being communicated to CASAL? 
I can't find fish being measured anywhere in casal output.
CONCLUSION: This is because in para\$ass\$sample_years, catchlen == 0 for all years.



In Burch, et. al, "Within CASAL, releases-at-length of tagged fish were converted to releases-at-age via a
length-at-age conversion matrix assuming a von Bertalanffy growth function and parameters
from Table 1. Estimated recaptures-at-length were obtained by applying the same length-at-age
conversion matrix to the estimated recaptures-at-age."
BUT, with the L_inf problem, how could this conversion matrix be calculated for fishL > L_inf? And how do I access this matrix?


Tried Growth L_inf = 2265
PERFORMED BAD.



Tried TOP growth with all other LHPs for TOA, and No catchA
PERFORMED BAD.



Should datass = datass instead of datass = para/$ass in run_complete_casal_assessment()?
NO I don't think so because all it uses from para is casal_path, inputprefix, mpd_dat, output_log, linux, intern. 
This means it can use para. THe only thing in the function that uses para$ass is specific_ratios which I don't use. see function for more. Note I'm using run_casal_pointest()


datass <- get_casal_data(Yr_current=om$years[y], datass=datass, om=om, sampling=sampling, obs=obs, tag=tag, mod=mod)
This part of the code exists right before the creation of CASAL input files. datass is used in the input files.
Does get_casal_data() work like it should?


create_casal_file_est(params=datass, casal_path=ctrl\$casal_path, skel_csl=ctrl\$est_skel_csl, csl=ctrl\$est_csl)
Does the input datass accuratly transfer stuff to the estimation file?
Compare datass to read.casal.est.file()



Try TOA_bug_1 without plus group.
CONCLUSION: no effect.

Try logistic selectivity with lower (5) X50:
CONCLUSION: BAD.


Change recruitment YCS to not be estimated:
Tried changing prior bounds in para\$ass\$estim_recruitment.YCS: 
CONCLUSION: Not translating to casal_out.log. Not even translating into datass before assessment files created. 


Try changing to B0 est method = "stoch"
Didn't change anything


Try changing to B0 est method = "init_age"
Didn't change much, got a little worse




  
  
### After meeting with Paul 12/6
Try another set of LHPs, maybe mackrel (short lived)
TOA_bug_3.R - skipjack tuna
CONCLUSION: They agree pretty well, except for overestimation of SSB0. The precision is extremely good. I think this is because there are very many tagged fish being recaptured.
DOUBLE CHECK THIS WITH MORE ITERATIONS
With 200 iterations, there is POOR agreement, even with my calculation of SSB! This is really bad because it means I cannot use my calc of SSB for just any species. It may only work for TOA for the scenario I tried!



Fork Planetfish DONE

Look at casal manual for phases of estimation. 
Is YCS estimated along with other parameters? is it estimated on it's own?

Look at res\$tags for numbers at age of RELEASE as well as recaptures

Propose plan for Paul

Make more diagnostic plot functions to explore the om results vs am results.
Generalize these to accept multiple types of data.
Made some in diagnostics.R


Add switch that creates csl files but doesn't run the assessment.
para\$control\$pin_generate_casal_files
CONCLUSION: didn't do this but added switch to save datass
REASON: If save csl files and don't run assessment, user will not know if the assessment will work.
I can always run the assessment one time to generate csl files, but I really need the datass object to compare, 
hence the utility in saving it. Also, the output_log file contains important stuff that the csl files do not.


YCS.
I changed the estimate YCS parameters to all be 1. I commented out the position in M3_CASAL1_Data.r where the parameters were over-written to allow full transmission to the casal csl files. 
CONCLUSION: this had the intended effect: the numbers at age between the OM and AM agree very nicely now. 
PROBLEM: SSB is still being under-estimated by the am after 30 iterations. How could this be?
  
  
  
  
Should the tagged fish be a negligible fraction of the total fish population without an impact of the population abundance or mortality?
(Burch et al. 2017 says this)


Why is SSB calculated before 2nd half of natM in OM but in Burch et al. 2017 it says it is calculated at the end of the year's processes?
I changed this to be calculated at the very end of OM loop, The discrepency was lessened as the OM SSB generally decreased. However, there was still a consistent discrepency. 
I tried manually calculating SSB (see below) for the OM and it does better at matching the AM for initial 
  
  
Try lowering catch to 1000 tonnes
Manual OM SSB matches casal SSB mutch better!


Try calculating SSB at end of run_annual_om() loop again but without h_species.
This had better agreement with AM but did not match exactly with my manual SSB. How could this be?
Ran again with 200 runs and there wasn't great agreement between OM and AM SSB but there was pretty good
agreement between the manual and built in OM SSB. WFT?


Try reverting back to the original built-in SSB method.
this is better I think, just ignore it's calculation and calculate my own SSB...?
Would this effect next year's recruitment calculation?


Try increasing tags to 4500 and tag duration to 10 years to see if SSB estimation improves:
YES, it improves, it is spot on with initial, but off a little with current SSB. 


Try with TOP updated LHPs - TOA_bug_4.R     100 iters
It does OK with internal SSB calculation but not great. 
It does better with my SSB calculation. It does really well with current, but not as well with initial.


Try with TOP updated LHPs but with old Growth - TOA_bug_4.R    201 iters
It does better than above with internal SSB calc, but much worse with my SSB calc
Along with the trial for Skipjack Tuna, This means that my calc SSB method is not reliably better or accurate. 
  
  

Try changing assessment years.
Current problem: tag recaptures not showing up in outputlog.
come back to it at: datass.TOA\$Rec_data  why aren't there recaptures?? look at M3_CASAL1_Data.r


Messing with para\$ass\$spawning_part_mort <- 0.5
Worked well for TOA_bug_4.R
Didn't work for TOA_bug_2.R
Didn't work for TOA_bug_3.R

## population.csl Questions
Should \@size_based False be True in population.csl?
I think it should be False because this is a age-based model.
  
  
  
  
  
  
  
  
## estimation.csl Questions

Do datass input parameter and estimation.csl line up?

### TOA

```{r, echo=F}
library(casal)
library(earthfish)
# datass.TOA = readRDS("C:/Users/STA384/Documents/GitHub/planetfish2_bugs/Comparisons/datass_TOA_6_6_19")
# datass.TOA = readRDS("C:/Users/STA384/Documents/GitHub/planetfish2_bugs/Output/TOA_bug_2/datass.Rds")
datass.TOA = readRDS("C:/Users/STA384/Documents/GitHub/planetfish2_bugs/Output/TOA_bug_2/datass.Rds")
# estimation = extract.csl.file("C:/Users/STA384/Documents/GitHub/planetfish2_bugs/Output/TOA_bug_2/casal_estimation.csl")
estimation = extract.csl.file("C:/Users/STA384/Documents/GitHub/planetfish2_bugs/Output/TOA_bug_2/casal_estimation.csl")
# population.TOA = extract.csl.file("C:/Users/STA384/Documents/GitHub/planetfish2_bugs/Output/TOA_bug_2/casal_population.csl")
population.TOA = extract.csl.file("C:/Users/STA384/Documents/GitHub/planetfish2_bugs/Output/TOA_bug_2/casal_population.csl")

size.class = datass.TOA$class_mins[-length(datass.TOA$class_mins)]

## TAGS RECAPTURED
tags.2009.om = datass.TOA$Rec_data$Tags2009_R1_R1
tags.2009.am = estimation$`tag_recapture[Tags2009_R1_R1]`$recaptured_2010

plot(size.class, tags.2009.om, ylab = "Frequency", xlab = "Size")
points(size.class, tags.2009.am, col = "red", pch = 3)
legend("topright", legend = c("OM", "AM"), pch = c(1, 3), col = c("black", "red"), title = "Tags Recaptured")


## FISH SCANNED
tags.2009.om = datass.TOA$scannedN$Tags2009_R1_R1
tags.2009.am = estimation$`tag_recapture[Tags2009_R1_R1]`$scanned_2010

plot(size.class, tags.2009.om, ylab = "Frequency", xlab = "Size")
points(size.class, tags.2009.am, col = "red", pch = 3)
legend("topright", legend = c("OM", "AM"), pch = c(1, 3), col = c("black", "red"), title = "Fish Scanned")


## CATCH AT AGE FREQUENCY
age.om = datass.TOA$catch_age$LL[,"2010",1,1,1]
age.am = as.numeric(estimation$`catch_at[LL_catchA]`$`2010`)

plot(age.om, ylim = c(0, 150), ylab = "Frequency", xlab = "Age")
points(age.am*500, col = "red", pch = 3)
lines(100*ogive("double_normal", 1:35, params = list(top=10, sigma_left=2, sigma_right=10)))


## COMBINED AGE (from catch_age) AND LENGTH (from scanned fish)
tags.2009.om = datass.TOA$scannedN$Tags2009_R1_R1
tags.2009.am = estimation$`tag_recapture[Tags2009_R1_R1]`$scanned_2010

plot(size.class, tags.2009.om, ylab = "Frequency", xlab = "Size")
points(size.class, tags.2009.am, col = "red", pch = 3)
points(calc_VBlen(datass.TOA$ages, rep(NA, 35), datass.TOA$estgrowth[[1]]), age.om*250, col = "blue")
points(calc_VBlen(datass.TOA$ages, rep(NA, 35), datass.TOA$estgrowth[[1]]), age.am*150000, col = "blue", pch = 3)
legend("topright", legend = c("OM Scanned", "AM Scanned", "OM catchA", "AM catchA"), pch = c(1, 3), col = c("black", "red", "blue", "blue"))


## POPULATION OM AGE FREQUENCY VS AM ESTIMATED AGE FREQUENCY
res.TOA = readRDS("C:/Users/STA384/Documents/GitHub/planetfish2_bugs/Output/TOA_bug_2/res.Rds")
output.TOA = extract.quantities("C:/Users/STA384/Documents/GitHub/planetfish2_bugs/Output/TOA_bug_2/casalout_output.log")
est.age.om = res.TOA$pop$n[,,1,,]*2
est.age.am = output.TOA$Numbers_at_age_R1

plot(est.age.om[,"1990"], ylim = c(0, 1e6))
points(est.age.am$`1990`, col = "red")

plot(est.age.om[,"2009"])
points(est.age.am$`2009`, col = "red")

for (i in 1:21) {
  plot(est.age.om[,i], main = paste0("Year ", i), xlab = "Age", ylab = "Number in Population")
  points(est.age.am[[i]], col = "red", pch = 3)
  legend("topright", legend = c("OM", "AM"), pch = c(1, 3), col = c("black", "red"))
}


## CALCULATE SSB BY HAND AND COMPARE
2*sum(res.TOA$pop$n[,"1990",1,1,1] * (1-0.5*res.TOA$mod$h_species[,"1990",1,1,1]) * res.TOA$pop$wt[,"1990",1,1,1] * res.TOA$pop$fec[,"1990",1,1,1])
2*res.TOA$mod$ssb[,"1990",1,1,1] # Same as res.TOP$mod$ssb0
# Why are the two above different? -> look into it in run_annual_om()

sum(est.age.am$`1990` * res.TOA$pop$wt[,"1990",1,1,1] * res.TOA$pop$fec[,"1990",1,1,1])



## TAGS RELEASED
tags.2007.om = rowSums(res.TOA$tag$tags[,"2007",,1,1,"2007",1]) # by age, summed over sex
tags.2007.am = as.numeric(population.TOA$`tag[Tags2007_R1_LL]`$number) * as.numeric(population.TOA$`tag[Tags2007_R1_LL]`$props_all) # by length bin
sum(tags.2007.om)
sum(tags.2007.am)
####### WHY AREN't THE OM TAGS SUMMING TO 2500???
# I think because tag shedding rate and natural mortality is applied?



## TAGS RELEASED FROM DATASS?




```

### Hard Calculate SSB
This r section loads the age frequency data from a single OM and AM run and calculates the SSB with my function.
It uses the res.Rds results from the OM and the casalout_output.log results from the AM.

```{r}
## POPULATION OM AGE FREQUENCY VS AM ESTIMATED AGE FREQUENCY
res.TOA = readRDS("C:/Users/STA384/Documents/GitHub/planetfish2_bugs/Output/TOA_bug_2/res.Rds")
para.TOA = readRDS("C:/Users/STA384/Documents/GitHub/planetfish2_bugs/Output/TOA_bug_2/para.Rds")
output.TOA = extract.quantities("C:/Users/STA384/Documents/GitHub/planetfish2_bugs/Output/TOA_bug_2/casalout_output.log")
output.TOA2 = read.csv("C:/Users/STA384/Documents/GitHub/planetfish2_bugs/Output/TOA_bug_2/TOA_bug_2_Niter_300.csv")
est.age.om = res.TOA$pop$n[,,1,,]*2
est.age.am = output.TOA$Numbers_at_age_R1




SSB.om = calc_SSB("res", est.age.om, para.TOA$om$growth$f, para.TOA$om$WL$f, para.TOA$om$pin_mat, para.TOA$om$maturity$f)
SSB.am = calc_SSB("output_log", est.age.am, para.TOA$om$growth$f, para.TOA$om$WL$f, para.TOA$om$pin_mat, para.TOA$om$maturity$f)
SSB.am2 = output.TOA2[, grep("AM_ssb_", colnames(output.TOA2))]
SSB.om2 = as.numeric(output.TOA2[nrow(output.TOA2), grep("OM_ssb_R1", colnames(output.TOA2))])

# All the things
plot(SSB.om, ylim = c(10000, 60000), main = "SSB Calculated Manually")
points(SSB.am, col = "red", pch = 3)
points(as.numeric(SSB.am2[nrow(output.TOA2), ]), col = "red")
points(SSB.om2, pch = 3)
legend("topright", legend = c("Earthfish OM SSB", "Manual OM SSB", "Casal SSB", "Manual Casal SSB"), pch = c(3, 1, 1, 3), col = c("black", "black", "red", "red"))


# Just my manual om SSB and casal SSB distribution
plot_SSB(output.TOA2, item = "AM_ssb_", mean = F, ylim = c(9000, 60000))
points(SSB.om, pch = 3, col = "red")


# relative error
par(mfrow = c(1,3))
boxplot((SSB.am2[, ncol(SSB.am2)] - SSB.om[length(SSB.om)]) / SSB.om[length(SSB.om)], main = "current", ylim = c(-0.22, 0.02))
boxplot((SSB.am2[, 1] - SSB.om[1]) / SSB.om[1], main = "initial", ylim = c(-0.22, 0.02))
boxplot((SSB.am2[, ncol(SSB.am2)]/SSB.am2[, 1] - SSB.om[length(SSB.om)]/SSB.om[1]) / SSB.om[length(SSB.om)]/SSB.om[1], main = "status", ylim = c(-0.22, 0.02))

```


CONCLUSION: How on earth does the operating model and subsequently assessment model know the selectivity in length if I provided it in age?
If it knows it in age, it must have converted it to length somehow to get these proportion scanned and recaptured fish by length. 
IT CAN GET LENGTHS FROM AGES via VB function. The function cannot get ages from lengths.


#### Calculating lengths from ages

```{r}


ssages.TOA = seq(1.5, 35.5, 1)
len_classes.TOA = seq(100, 2000, 50)

round(sample_lengths(ssages, sampling$len_classes, dat_age1[,y], om$growth[[om$sex[i]]]), 1)



```





Why does datass.TOA\$survey_age_n exist when there is no survey age stuff in para\$om?



### TOP
```{r, echo=F}
datass.TOP = readRDS("C:/Users/STA384/Documents/GitHub/planetfish2_bugs/Comparisons/datass_TOP_6_6_19")
estimation = extract.csl.file("C:/Users/STA384/Documents/GitHub/planetfish2_bugs/Comparisons/casal_estimation_TOP.csl")
size.class = datass.TOP$class_mins[-length(datass.TOP$class_mins)]

## TAGS RECAPTURED
tags.2009.om = datass.TOP$Rec_data$Tags2009_R1_R1
tags.2009.am = estimation$`tag_recapture[Tags2009_R1_R1]`$recaptured_2010

plot(size.class, tags.2009.om)
points(size.class, tags.2009.am, col = "red", pch = 3)


## TAGS SCANNED
tags.2009.om = datass.TOP$scannedN$Tags2009_R1_R1
tags.2009.am = estimation$`tag_recapture[Tags2009_R1_R1]`$scanned_2010

plot(size.class, tags.2009.om)
points(size.class, tags.2009.am, col = "red", pch = 3)


## CATCH AT AGE FREQUENCY
age.om = datass.TOP$catch_age$LL[,"2010",1,1,1]
age.am = as.numeric(estimation$`catch_at[LL_catchA]`$`2010`)

plot(age.om, ylim = c(0, 150))
points(age.am*500, col = "red", pch = 3)
lines(500*ogive("double_normal", 1:30, params = list(top=10, sigma_left=2, sigma_right=10)))

## COMBINED AGE (from catch_age) AND LENGTH (from scanned fish)
tags.2009.om = datass.TOP$scannedN$Tags2009_R1_R1
tags.2009.am = estimation$`tag_recapture[Tags2009_R1_R1]`$scanned_2010

plot(size.class, tags.2009.om, ylab = "Frequency", xlab = "Size")
points(size.class, tags.2009.am, col = "red", pch = 3)
points(calc_VBlen(datass.TOP$ages, rep(NA, 30), datass.TOP$estgrowth[[1]]), age.om*1700, col = "blue")
points(calc_VBlen(datass.TOP$ages, rep(NA, 30), datass.TOP$estgrowth[[1]]), age.am*800000, col = "blue", pch = 3)
legend("topright", legend = c("OM Scanned", "AM Scanned", "OM catchA", "AM catchA"), pch = c(1, 3), col = c("black", "red", "blue", "blue"))



## POPULATION OM AGE FREQUENCY VS AM ESTIMATED AGE FREQUENCY
res.TOP = readRDS("C:/Users/STA384/Documents/GitHub/planetfish2_bugs/Comparisons/res_TOP_31_5_19")
output.TOP = extract.quantities("C:/Users/STA384/Documents/GitHub/planetfish2_bugs/Comparisons/casalout_output2_TOP_11_6_19.log")
est.age.om = res.TOP$pop$n[,,1,,]*2
est.age.am = output.TOP$Numbers_at_age_R1

plot(est.age.om[,"1990"], ylim = c(0, 1.7e7))
points(est.age.am$`1990`, col = "red")

plot(est.age.om[,"2009"], ylim = c(0, 1.7e7))
points(est.age.am$`2009`, col = "red")

for (i in 1:21) {
  plot(est.age.om[,i], main = paste0("Year ", i), xlab = "Age", ylab = "Number in Population")
  points(est.age.am[[i]], col = "red")
  legend("topright", legend = c("OM", "AM"), pch = c(1, 3), col = c("black", "red"))
}


## CALCULATE SSB BY HAND AND COMPARE
2*sum(res.TOP$pop$n[,"1990",1,1,1] * (1-0.5*res.TOP$mod$h_species[,"1990",1,1,1]) * res.TOP$pop$wt[,"1990",1,1,1] * res.TOP$pop$fec[,"1990",1,1,1])
2*res.TOP$mod$ssb[,"1990",1,1,1] # Same as res.TOP$mod$ssb0
# Why are the two above different? -> look into it in run_annual_om()

sum(est.age.am$`1990` * res.TOP$pop$wt[,"1990",1,1,1] * res.TOP$pop$fec[,"1990",1,1,1])



output.TOP$SSBs$SSB


```







Does res\$fleet stuff = res\$obs stuff?

```{r}
res.TOA = readRDS("C:/Users/STA384/Documents/GitHub/planetfish2_bugs/Comparisons/res_TOA_31_5_19")

# Catch Selectivity = tag Selectivity?
res.TOA$fleet$LL1$landings_sel[,,1,1,1] - res.TOA$obs$LL1$tag_sel[,,1,1,1]
# CONCLUSION: YES
```


Does res\$fleet stuff = res\$obs stuff?

```{r}
res.TOA = readRDS("C:/Users/STA384/Documents/GitHub/planetfish2_bugs/Comparisons/res_TOA_31_5_19")

# Selectivity
res.TOA$fleet$LL1$landings_sel[,,1,1,1] - res.TOA$fleet$LL1$landings_sel[,,1,1,1]
# CONCLUSION: YES
```













Does \@catch_at LL_catchA add up to 1000 every year?

```{r, echo=F}
estimation = extract.csl.file("C:/Users/STA384/Documents/GitHub/planetfish2_bugs/Output/TOA_bug_1/casal_estimation.csl")
temp = as.numeric(estimation$`catch_at[LL_catchA]`$`2000`) # this is a proportion at age class.

sum(temp)

```
CONCLUSION: Undetermined. Only gives proportion, not quantity of fish. Can compare this frequency to selectivity possibly?
In any case, still need to find where catchA numbers are reported in CASAL files.




Do scanned fish in \@tag_recapture Tags2005_R1_R1 add up to 6000 tonnes?

```{r, echo=F}
class_mins = as.numeric(estimation$`tag_recapture[Tags2005_R1_R1]`$class_mins)
scanned    = as.numeric(estimation$`tag_recapture[Tags2005_R1_R1]`$scanned_2006)

plot(class_mins[-length(class_mins)], scanned)



```
CONCLUSION: I need to convert length to wight to answer this question. I think this process requires length to age to weight calculation, but length to age is the inverse of Von Bertalanffy which cannot take L>L_inf. This is a problem if any length classes exceed L_inf, which they do. 




Does frequency of scanned fish in \@tag_recapture Tags2005_R1_R1 match fishing selectivity? i.e. does tagging selectivity match fishing selectivity?







## Things I'd like to change in Planetfish
 * allow assessment model year flexibility
 * allow turning off of YCS and q.










## Warnings

Warning message:
In get_casal_data(Yr_current = om$years[y], datass = datass, om = om,  :
  Metiers in OM that are not included in Assessment: LL1
CONCLUSION: this warning shows up in Paul's stuff and mine.



In casal.string.to.vector.of.numbers(casal.remove.first.words(lines[i],  ... :
  NAs introduced by coercion
CONCLUSION: Ask Paul...
